How to Deal With Measurement Error in Measurement Models

### 2023-03-20 paper.qmd
big commit

```{=tex}
\usetikzlibrary{positioning}
\tikzset{
    > = stealth,
    every node/.append style = {
        draw = none
    },
    every path/.append style = {
        arrows = ->
    },
    hidden/.style = {
        draw = black,
        shape = circle,
        inner sep = 1pt
    }
}
```
# Introduction

@@

>>>>

```{=tex}
\usetikzlibrary{positioning}
\tikzset{
    > = stealth,
    every node/.append style = {
        draw = none
    },
    every path/.append style = {
        arrows = ->
    },
    hidden/.style = {
        draw = black,
        shape = circle,
        inner sep = 1pt
    }
}
```

# Introduction

@@

```{r}
#| eval: false
p1 <- tibble(race = rep(c("AAPI", "Black", "Hispanic", "Native\nAmerican", "White"), 3),
       probs = round(
         c(MCMCpack::rdirichlet(1, c(1, 1, 20, 1, 1)),
           MCMCpack::rdirichlet(1, c(1, 1, 10, 1, 10)),
           MCMCpack::rdirichlet(1, c(5, 5, 8, 5, 5))), 
         3),
       model = c(rep("a", 5),
                 rep("b", 5),
                 rep("c", 5))) |> 
  ggplot(aes(x = probs, y = model, fill = race)) +
  geom_bar(stat = "identity") +
  scale_fill_met_d("Cross") +
  theme_void() +
  theme(legend.position = "none")

p2 <- ggplot() +
  stat_function(fun = dnorm,
                args = list(sd = 1), 
                geom = "area", fill = met.brewer("Cross")[[7]], alpha = 1) +
    stat_function(fun = dnorm,
                args = list(sd = 1), 
                color = "white", linewidth = 1, linetype = "solid") +
  xlim(-9, 9) +
  theme_void()

p3 <- ggplot() +
  stat_function(fun = dnorm,
                args = list(sd = 3), 
                geom = "area", fill = met.brewer("Cross")[[7]], alpha = 1) +
  stat_function(fun = dnorm,
                args = list(sd = 3), 
                color = "white", linewidth = 1, linetype = "solid") +
  xlim(-9, 9) +
  theme_void()

p4 <- ggplot() +
  stat_function(fun = sn::dsn,
                args = list(alpha = -3, omega = 3, xi = 3), 
                geom = "area", fill = met.brewer("Cross")[[7]], alpha = 1) +
  stat_function(fun = sn::dsn,
                args = list(alpha = -3, omega = 3, xi = 3), 
                color = "white", linewidth = 1, linetype = "solid") +
  xlim(-9, 9) +
  theme_void()

p1 + (p2 / p4 / p3)
```
